---
title: "PackToTheFuture"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{PackToTheFuture}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PackToTheFuture)
```

### Introduction

The **`PackToTheFuture`** package is designed to streamline data-science workflows related to the Central Dogma of Molecular Biology applied in a bioinformatics contexts. Specifically, it provides the following functions:

-   function 1 –\> `create_seq()`

-   function 2 –\> `get_rna()`

-   function 3 –\> `get_codons()`

-   function 4 –\> `traduction_prot()`

-   function 5 –\> `plot_base_seq()`

In the following, we will go through each function in the package one by one and show how to use them together in a workflow. Finally we discuss typical use cases and potential future enhancements.

### Function 1

Ákos types here.

### Function 2

Elvin types here.

### Function 3

Joshua types here.

```{r}
get_codons <- function(seq, start = 1){
  seq_len <- nchar(seq)
  codons <- substring(seq,
                      first = seq(from = start, to = seq_len-3+1, by = 3),
                      last = seq(from = 3+start-1, to = seq_len, by = 3))
  return(codons)
}
```

### Function 4

Marcel types here.

### Function 5

Mikel types here.

### Possible use cases

Who types here?
