---
title: "PackToTheFuture"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{PackToTheFuture}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PackToTheFuture)
```

### Introduction

Everyone creates their own branch and edits their section. Joshua will do the introduction.

### Function 1

Ákos types here.

### Function 2

Elvin types here.

### Function 3

Joshua types here.

### Function 4 (`create_seq()`)

*Purpose*: Generate a random sequence composed of nucleotides A, T, G, and C.

Function definition:

```{r}
create_seq <- function(seq_size){
  seq_list <- sample(c("A", "T", "G", "C"), size = seq_size, replace = TRUE)
  seq_str <- paste0(seq_list, collapse = "")
  return(seq_str)
}
```

#### Parameters

| Argument |  Type   |            Description             |
|:--------:|:-------:|:----------------------------------:|
| seq_size | numeric | Length of the sequence to generate |

#### Returns

A character string representing a DNA sequence.

#### Example usage

``` r
# Generate a sequence of length 12
seq1 <- create_seq(12)
seq1
```

Expected output format:

``` r
"ATGCGTACGTTA"
```

Each call produces a new random sequence of the same general format.

### Function 5

Mikel types here.
